Outstanding Title

### 2017-04-05 writing/EpiDraft.Rmd
Obtain and tidy Legionnaire's data

>>>>

##Legionnaire's Example

Here is a plot of weekly counts of Legionnaire's disease in the United States from 2014 through 2016. This data was obtained from the CDC website.

```{r, echo=FALSE}
#I used the variable "Legionellosis, Current week" so hopefully that's right
leg1 <- read.csv("~/eesim/Legionnaires data/2014Leg.csv")[,c(2,3,24)]
leg2 <- read.csv("~/eesim/Legionnaires data/2015Leg.csv")[,c(2,3,24)]
leg3 <- read.csv("~/eesim/Legionnaires data/2016Leg.csv")[,c(2,3,24)]
leg <- data.frame(year = c(leg1$MMWR.Year, leg2$MMWR.Year, leg3$MMWR.Year), week = c(leg1$MMWR.Week, leg2$MMWR.Week, leg3$MMWR.Week), cases = c(leg1$Legionellosis..Current.week, leg2$Legionellosis..Current.week, leg3$Legionellosis..Current.week))
plot(leg$cases, xlab = "Week", ylab = "Number of Cases", main = "Legionnaire's Disease 2014-2016")
```

We can pull the trend from this data:

```{r}
custom
```
